\documentclass[a4paper,10pt]{article}

\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{amssymb,amsmath}
\usepackage{listings}
\usepackage[titletoc]{appendix}
\usepackage{courier}
\usepackage[countmax]{subfloat}
\usepackage{here}
\usepackage{epstopdf}

\linespread{1}

\hoffset -1in \topmargin 0mm \voffset 0mm \headheight 0mm
\headsep0mm
\oddsidemargin  20mm     %   Left margin on odd-numbered pages.
\evensidemargin 20mm     %   Left margin on even-numbered pages.
\textwidth   170mm       %   Width of text line.
\textheight  252mm

\makeatletter
\renewcommand\@openbib@code{%
     \advance\leftmargin  \z@ %\bibindent
      \itemindent \z@
     % Move bibitems close together
     \parsep -0.8ex
     }
\makeatother

\makeatletter
\renewcommand\section{\@startsection {section}{1}{\z@}%
                                   {-3.5ex \@plus -1ex \@minus -.2ex}%
                                   {2.3ex \@plus.2ex}%
                                   {\large\bfseries}}
\makeatother

\makeatletter
\renewcommand\subsection{\@startsection {subsection}{1}{\z@}%
                                   {-3.5ex \@plus -1ex \@minus -.2ex}%
                                   {2.3ex \@plus.2ex}%
                                   {\normalsize\bfseries}}
\makeatother

\begin{document}
\pagestyle{empty}

\begin{center}
{\bf \Large REVISITED BOX COUNTING TECHNIQUE IN BAYESIAN SENSE}
\end{center}

\smallskip
\begin{center} % David Blatsk\'{y}$^1$,
{\large David Blatsk\'{y}$^1$, Jarom\'{i}r Kukal$^1$, V\'{a}clav Hubata--Vacek$^1$}
\end{center}

\smallskip
\begin{center}
$^1$CTU in Prague, Faculty of Nuclear Sciences and Physical Engineering\\
Department of Software Engineering \\
B\v{r}ehov\'{a} 7, 115 19 Prague 1 \\
Czech Republic\\
blatsdav@fjfi.cvut.cz\\
 ~\\

\end{center}

\bigskip
\noindent Abstract: \textit{Fractal patterns appear in a wide variety of sources across nature. The unusual characteristic of fractals is that they entail non-integer dimension. The Box Counting method is one of the often used approach to estimate the fractal dimension of a signal. Thanks to the relationship between entropy and the fractal dimension, it is possible to employ entropy in estimating the fractal dimension. In this paper, we propose to utilize Bayesian estimate of Hartley entropy of a finite sample in fractal dimension estimation. This method was tested on artificial fractals generated by recursive expansion of appropriate matrices.}

\vspace*{10pt} \noindent Keywords: \textit{unbiased estimation, Hartley entropy, Shannon entropy, Box Counting}


\bigskip

\input{revbox_01_Introduction.tex}

\input{revbox_02_NaiveEst.tex}

\input{revbox_03_BayesEstHartley.tex}

\input{revbox_04_BayesEstShannon.tex}

\input{revbox_05_RevisedBoxCounting.tex}

\input{revbox_06_ExpPart.tex}

\section {Conclusion}
In this paper we derived the Bayesian estimator $\hat{H}_{0,\mbox{\scriptsize{Bayes}}}$ of Hartley entropy for a general value of the parameter $\alpha^*$. As shown, similar approach can also be used to estimate Shannon entropy $\hat{H}_{1,\mbox{\scriptsize{Bayes}}}$. These both can result in less biased estimates of the appropriate entropy when used with proper $\alpha^*$ and the grid size $a$. According to the relation between fractal (information) dimension and Hartley (Shannon) entropy, we estimated dimensions from experimental data. The results turned out to be significantly more accurate than those estimated naively.


\vspace*{10pt} \noindent {\bf Acknowledgement:} The authors acknowledge the funding from the CTU in Prague, \\ Grant SGS14/208/OHK4/3T/14.

\input{revbox_bibliography.tex}

%\input{revbox_graphs.tex}

%\input{revbox_tables.tex}

\newpage

\end{thebibliography}
\begin{appendices}

\section {Appendix}


\input{revbox_app_derivation.tex}

\input{revbox_code.tex}


\end{appendices}



\end{document}
